---
title: "MemoryLeaks"
output: github_document
date: "2023-05-04"
knit: (function(input, ...) {
    callr::r(
        function(...) rmarkdown::render(...),
        args = list("MemoryLeak.Rmd", envir = globalenv()),
        show = T
    )
    })
---
```{r}
library(rextendr)
```

The below function reports memory usage at various times during the call of a Rust function.
By default we use an integer vector as the input, but the `vec` argument is customized ocasionally.

**Note that the actual error messages from extendr are shown here**.
```{r}
test_for_leaks <- function(func, vec = (1:10E7)[]){
  lobstr::mem_used() |> format() |> paste(" used before allocation") |> print()
  lobstr::mem_used() |> format() |> paste(" used after allocation") |> print()
  force(vec)
  func(vec) |> try(silent = TRUE) 
  lobstr::mem_used() |> format() |> paste(" used after panic") |> print()
  rm(vec)
  gc(verbose = FALSE)
  lobstr::mem_used() |> format() |> paste(" used after gc") |> print()
}
```


# Case 1

* `use_try_from` is false
* Panic with no message

```{extendrsrc}
#[extendr]
fn throw_1(x: Robj) {
    panic!()
}
```
```{r}
test_for_leaks(throw_1)
```
Definitely a leak.

# Case 2

* `use_try_from` is true
* Panic with no message

```{extendrsrc}
#[extendr(use_try_from = true)]
fn throw_2(x: Robj) {
    panic!()
}
```
```{r}
test_for_leaks(throw_2)
```

No leak!

```{r}
test_for_leaks(throw_2, vec = rep(LETTERS, 1E7))
```

But when using a string vector, it seems to leak.

# Case 3
* `use_try_from` is true
* Return string error

```{extendrsrc}
#[extendr(use_try_from = true)]
fn throw_3(x: Robj) -> Result<()> {
  Err(Error::Other(String::from("")))
}
```
```{r}
test_for_leaks(throw_3)
```

Also no leak!

```{r}
test_for_leaks(throw_3, vec = rep(LETTERS, 1E7))
```

As above, a string vector leaks.

# Case 4
* `use_try_from` is true
* Return error that takes a Robj

```{extendrsrc}
#[extendr(use_try_from = true)]
fn throw_4(x: Robj) -> Result<()> {
  Err(Error::ExpectedList(x))
}
```

```{r}
test_for_leaks(throw_4, vec = (1:1E5)[])
```

It's a bit hard to see from the small memory increase, but this is a leak.

```{r}
test_for_leaks(throw_4, vec = rep(LETTERS, 1E4))
```

As above.