---
title: "MemoryLeak2"
output: github_document
date: "2023-05-09"
knit: (function(input, ...) {
    callr::r(
        function(...) rmarkdown::render(...),
        args = list("MemoryLeak2.Rmd", envir = globalenv()),
    )
    })
---

```{r}
library(rextendr)
```

The idea of this function is to allocate a large vector, pass it to an extendr
function, then clean everything up and see if there is still an overall increase
in memory (a leak).
```{r}
test_for_leaks <- function(func, make_vec){
  initial = lobstr::mem_used()
  cli::cli_alert_info("{format(initial)} used before allocation")
  vec = make_vec()
  cli::cli_alert_info("{lobstr::mem_used() |> format()} used after allocation")
  func(vec) |> try(silent = TRUE)
  cli::cli_alert_info("{lobstr::mem_used() |> format()} used after function call")
  rm(vec)
  gc(verbose = FALSE)
  final = lobstr::mem_used()
  cli::cli_alert_info("{lobstr::mem_used() |> format()} used after gc")
  if ((final - initial) > 1E7){
    cli::cli_alert_danger("Leak detected!")
  }
}
```

A baseline for Rust:
```{extendrsrc}
#[extendr(use_try_from = true)]
fn identity_rust(x: Robj) -> Robj { x }
```

Panic, and no `try_from`:
```{extendrsrc}
#[extendr]
fn throw_1(x: Robj) { panic!() }
```

Panic, and yes `try_from`:
```{extendrsrc}
#[extendr(use_try_from = true)]
fn throw_2(x: Robj) { panic!() }
```

Throwing an error that doesn't hold a Robj, with `try_from`:
```{extendrsrc}
#[extendr(use_try_from = true)]
fn throw_3(x: Robj) -> Result<()> {
  Err(Error::Other(String::from("")))
}
```

Throwing an error that *does* hold a Robj, with `try_from`:
```{extendrsrc}
#[extendr(use_try_from = true)]
fn throw_4(x: Robj) -> Result<()> {
  Err(Error::ExpectedList(x))
}
```

A baseline that doesn't even use extendr:
```{r}
identity_r <- function(x) x
```

These functions each produce a large but random vector of each of the 4
primitive types:
```{r}
vecs = tibble::tribble(
  ~vec_name, ~make_vec,
  "integer", function() (1:1E7)[],
  "double", function() rnorm(1E7),
  "character", function() as.character(rnorm(1E7)),
  "logical", function() as.logical(rnorm(1E7))
)
```

Collect together all the functions we want to test:
```{r}
funcs = tibble::tribble(
  ~func_name, ~func,
  "r_identity", identity_r,
  "rust_identity", identity_rust,
  "throw_1", throw_1,
  "throw_2", throw_2,
  "throw_3", throw_3
)
```

And the main test loop. For each combination of test function and input vector,
we test for leaks:
```{r, results='hide'}
tidyr::expand_grid(vecs, funcs) |>
  purrr::pmap(function(vec_name, make_vec, func_name, func){
      cli::cli_alert_info("Testing {func_name} + {vec_name} for leaks")
      test_for_leaks(func, make_vec)
  })
```
